The Impact of Anthropogenic Forcing on ENSO Amplitude

### 2021-07-22 presentations/presentation_current/presentation.tex
presentation skeleton

% Created 2021-07-20 Tue 18:30
% Intended LaTeX compiler: pdflatex
\documentclass[presentation]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{natbib}
\renewcommand{\bibsection}{}
\usetheme{metropolis}
\author{Benjamin Goldman}
\date{\today}
\title{Presentation}
\hypersetup{
 pdfauthor={Benjamin Goldman},
 pdftitle={Presentation},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.5)}, 
 pdflang={English}}
\begin{document}

@@

\begin{frame}[label={sec:org6b28ed4}]{Test}
\end{frame}
\end{document}

>>>>

\documentclass{beamer}
\title{The Impact of Anthropogenic Forcing on ENSO Amplitude}
\author{Ben Goldman}
\date{\today}
\usepackage{natbib}
\usepackage{tikz}
\usetheme{metropolis}
\renewcommand{\bibsection}{}

\begin{document}

@@

\begin{frame}
  \frametitle{Climate Change}
  \citet{bjerknes1969atmospheric}

\end{frame}

\begin{frame}
  \frametitle{El Niño}

\end{frame}

\begin{frame}
  \frametitle{Climate Simulation}

\end{frame}

\begin{frame}
  \frametitle{ENSO in the Future}

\end{frame}

\begin{frame}
  \frametitle{Gap and Goal}

\end{frame}

\begin{frame}
  \frametitle{Research Questions}

\end{frame}

\begin{frame}
  \frametitle{signal and Noise}

\end{frame}

\begin{frame}
  \frametitle{Ensembles: CESM1 and CESM2}

\end{frame}

\begin{frame}
  \frametitle{R and Python tools}

\end{frame}

\begin{frame}
  \frametitle{Role of Mentor and Student}

\end{frame}

\begin{frame}
  \frametitle{Measuring ENSO}

\end{frame}

\begin{frame}
  \frametitle{Measuring ENSO Intensity}

\end{frame}

\begin{frame}
  \frametitle{ENSO is Becoming Stronger}

\end{frame}

\begin{frame}
  \frametitle{It's not That Simple}

\end{frame}

\begin{frame}
  \frametitle{Single Forcing Ensembles}

\end{frame}

\begin{frame}
  \frametitle{Influence of Aerosols and Greenhouse Gasses}

\end{frame}

\begin{frame}
  \frametitle{Correlation With Ocean Temperature}

\end{frame}

\begin{frame}
  \frametitle{Stratification}

\end{frame}

\begin{frame}
  \frametitle{Stratification in Other Ensembles}

\end{frame}

\begin{frame}
  \frametitle{References}
  \bibliographystyle{apalike}
  \bibliography{references.bib}
\end{frame}

\end{document}
